---
title: "Drug Visualization Tests"
author: "Sara Gosline"
date: "9/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Summary

We have data from a number of drugs across two plates and concentrations. How do we visualize this and summarize in a meaningful manner? 

```{r get data, warning=FALSE}
source("loadOrganoidData.R")

head(drugData)

dcounts <- drugData%>%group_by(Drug)%>%summarize(numSamps=n_distinct(Plate),Measurements=n_distinct(Concentration))%>%arrange(Drug)

dcounts%>%ggplot()+geom_bar(aes(y=Measurements))

```

Now we have the data we want to determine what we
## What do we see across different drugs?

Can we compare across different drugs? 

Let's first start with drugs that have more than one measurement.


```{r pressure, warning=FALSE}

drugData%>%
  left_join(dcounts)%>%
  subset(Measurements>1)%>%
  ggplot(aes(x=Drug,y=Mean_Viability,col=Concentration,shape=Plate))+geom_jitter()+scale_x_discrete(guide = guide_axis(angle = 90))+scale_colour_gradient(low=pal[1],high=pal[2])+ggtitle('Drugs with more than one concentration')


drugData%>%
  left_join(dcounts)%>%
  subset(Measurements>1)%>%
  ggplot(aes(x=Drug,y=Mean_Zscore,col=Concentration,shape=Plate))+geom_jitter()+scale_x_discrete(guide = guide_axis(angle = 90))+scale_colour_gradient(low=pal[1],high=pal[2])+ggtitle('Drugs with more than one concentration')

```

Staurosporine seems to be effective, and Cobimetinib in the better screen. Some other ones around 60% seem promising. 

What if we look across all concentrations to see what had a hit rate less than 60? Or Zscore less than -1?

```{r hit rate, warning=FALSE}

drugData%>%
  subset(Mean_Viability<60)%>%
  ggplot(aes(x=Drug,y=Mean_Viability,col=Concentration,shape=Plate))+geom_jitter()+scale_x_discrete(guide = guide_axis(angle = 90))+scale_colour_gradient(low=pal[1],high=pal[2])+ggtitle('Drugs with more than 40% effect')


drugData%>%
  subset(Mean_Zscore<(-1))%>%
  ggplot(aes(x=Drug,y=Mean_Zscore,col=Concentration,shape=Plate))+geom_jitter()+scale_x_discrete(guide = guide_axis(angle = 90))+scale_colour_gradient(low=pal[1],high=pal[2])+ggtitle('Drugs with Z score lower than -1')
```

Ok are there any differences between mammocult and stempro treatment?? Here are the top 4 drug candidates.

```{r diff}

diffd=drugData%>%
  left_join(dcounts)%>%
  subset(numSamps>1)%>%
  group_by(Plate,Drug)%>%
  summarize(minZ=min(Mean_Zscore))%>%pivot_wider(values_from=minZ,names_from = Plate)%>%mutate(diff=abs(`NF1 PP14 S-C`-`NF1 PP14 M-C`))%>%arrange(diff)

drugData%>%
  subset(Drug%in%diffd$Drug)%>%
  mutate(group=paste(Plate,Drug))%>%
  ggplot(aes(x=Concentration,y=Mean_Zscore,col=Drug,shape=Plate))+scale_color_manual(values=pal)+geom_point()+geom_line(aes(group=group,alpha=0.6))+ggtitle("Differences between treatments")

```

Now we can take the drugs and see what genes are differentially expressed between the two conditions (mammocult and stempro). 

```{r difex}

m.conds<-subset(annotes,Media%in%c('Mammo'))%>%rownames()
s.conds<-subset(annotes,Media=='StemPro')%>%rownames()

res=limmaTwoFactorDEAnalysis(mat,m.conds,s.conds)%>%
    dplyr::arrange(P.Value)
  mres<-subset(res,adj.P.Val<0.05)
  numGenes= nrow(mres)

```
